---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ParlAT: Accessing Open Data of the Austrian Parliament

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public..](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

The ParlAT package seeks to provide an easy way for R users to access the Open Data offered by the Austrian Parliament. By leveraging the
Parliament’s API, it allows users to retrieve data on a wide range of issues such as legislative proposals, committee reports, details on MPs and their mandates, or parliamentary sessions. The package is designed to provide a consistent interface for accessing different datasets. For an introductory overview and some examples, please see the "Get started" section. For details, consult the functions' documentation under "References".

Please note that the package is **in a development stage**. So until it 
has reached a mature state, upcoming changes may break existing code. If you encounter any bug etc., you are welcome to 
file a pertaining issue at the package's [github repo](https://github.com/werkstattcodes/ParlAT/issues){target="_blank"}.

Also note that neither the package nor its author is affiliated to the Austrian Parliament.


## Installation

You can install ParlAT from [GitHub](https://github.com/) with:


```{r, eval=F}
# install.packages("pak")
pak::pak("werkstattcodes/ParlAT")
```

To install the latest development version from the dev branch use

```{r, eval=F}
pak::pak("werkstattcodes/ParlAT@dev")
```


## The Open Data Offer of the Austrian Parliament

The Open Data offer of the Austrian Parliament comprises [25 datasets](https://www.parlament.gv.at/recherchieren/open-data/daten-und-lizenz/index.html){target="_blank"} which are
made available - with some exceptions - under a CC BY 4.0 license. These datasets
are accessible via the search interface of the Austrian Parliament website as
well as by directly querying the Parliament's API. ParlAT seeks to facilitate
accessing the latter.

Mirroring the structure of the API, some of ParlAT's functions cover more than
one dataset. Other functions are specific to a single dataset. In addition, ParlAT 
offers several additional utility functions which either render the raw
output provided by Parliament's API more amenable for further processing or
return results which are likely to be of interest for the user but are not directly returned
by the API (see [references](#references) for details).

### Datasets and pertaining functions by ParlAT

Below a raw tabuliation of the Parliament's 25 open datasets and the ParlAT's pertaining
function to access it. Please note that this is only subset of the available parameters. 
For details see the function documentation in the reference section.

| Dataset                                                              | ParlAT Function                                            |
|----------------------------------------------------------------------|-----------------------------------------------------------|
| Anträge (Motions)                                                    | `get_items(item="ANTR")`                                   |
| Ausschussberichte (Committee reports)                                | `get_items(item="AUB")`                                    |
| Beschlüsse (Decisions)                                               | `get_items(item="BNR")`                                    |
| Gesetzesanträge des Bundesrates (Legislative Proposals of the Federal Council)   | `get_items(item="GABR")`                       |
| Regierungsvorlagen (Government Bills)                                | `get_items(item="RV")`                                     |
| Aktuelle Beiligungen (Current calls for public participation)        | `get_participation(active="J")`                            |
| Bürgerinitiativen (Citizen Initiatives)                              | `get_items(item="BI")`                                     |
| Petitionen (Petitions)                                               | `get_items(item="PET")`                                    |
| Stenographisches Protokolle (Session transcripts)                    | `get_transcripts()`                                        |
| Plenarsitzungen (Plenary sessions)                                   | `get_plenary_sessions()`                                   |
| Parlamentarier seit 1918 (MPs since 1918)                            | `get_mps()`                                                |
| Aktuelle Abg. z NR (Current members of National Council)             | `get_mps_current(institution="Nationalrat")`               |
| Aktuelle Abg. z BR (Current members of National Council)             | `get_mps_current(institution="Bundesrat")`                 |
| Parlamentskorrespondenz (Corrspondance)                              | not yet implemented                                        |
| Termine (Events)                                                     | `get_events()`                                             |
| Ausschüsse (Committees)                                              | `get_committees()`                                         |
| Ausschussmitgliedschaften (Committee membership)                     | `get_mps_details(..., detail_type="committees")`           |
| Schriftliche Anfragen NR (Written questions National Council)        | `get_items(item="J_JPR_M", institution="Nationalrat")`     |
| Schriftliche Anfragen BR (Written questions Federal Council)         | `get_items(item="J_JPR_M", institution="Bundesrat")`       |
| Stellungnahmen im EU-Hauptausschusses (Statements of the EU Main Committee) | `get_items(item="EU", type_eu_submission="S", institution="NR")` |
| Mitteilungen des EU-Unterausschusses (Communications of the EU Subcommittee)| `get_items(item="EU", type_eu_submission="MTEU", institution="NR")` |
| Stellungnahmen des Ständigen Unterausschusses des Hauptausschusses (Statements of the Permanent Subcommittee of the Main Committee)  | not yet implemented |
| Begründete Stellungnahmen des EU-Ausschusses (Reasoned Opinions of the EU Committee)| `get_items(item="EU", type_eu_submission="SBPL-BR", institution="BR")` |
| Mitteilungen des EU-Ausschusses BR (Communications of the EU Committee - Federal Council)| `get_items(item="EU", type_eu_submission="MT-BR", institution="BR")` |
| Stellungnahmen des EU-Ausschusses BR (Statements of the EU Committee Federal Council)| `get_items(item="EU", type_eu_submission="S-BR", institution="BR")` |


## References

<!--  -->