---
title: "Examples"
format: html
---

# Who spoke about what, and how does it compare to others?

This example compares the topics of parliamentary items where selected MPs personally contributed in plenary debates.

```{r}
#| label: setup
#| include: false

library(ParlAT)
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(forcats)
library(ggplot2)
library(scales)
library(RColorBrewer)
```

```{r}
#| label: helpers
#| include: false

get_pad_intern("Götze")

collect_mp_spoken_items <- function(pad_intern, institution = "NR") {
  
  pad_intern <- "5654"
  institution <- "NR"
  
  pad_intern <- as.character(pad_intern)

  df_plenary <- get_mps_details(
    pad_intern = pad_intern,
    detail_type = "plenary",
    institution = institution,
    echo = FALSE
  )

  if (is.null(df_plenary) || nrow(df_plenary) == 0) {
    return(list(
      spoken_items = tibble(),
      diagnostics = list(
        pad_intern = pad_intern,
        mp_name = NA_character_,
        mp = pad_intern,
        unmatched_meetings = character(),
        failed_items = character(),
        failed_periods = character()
      )
    ))
  }

  mp_name <- df_plenary |>
    filter(!is.na(name), name != "") |>
    count(name, sort = TRUE) |>
    slice_head(n = 1) |>
    pull(name)

  if (length(mp_name) == 0) {
    mp_name <- pad_intern
  }

  mp <- str_extract(mp_name, "\\S+$")

  periods <- df_plenary |>
    distinct(legis_period) |>
    mutate(period = as.integer(as.roman(legis_period))) |>
    filter(!is.na(period)) |>
    pull(period)

  meeting_results <- periods |>
    map(\(period) {
      safely(get_plenary_meetings)(
        institution = institution,
        legis_period = period,
        meeting_and_activities = "activities",
        echo = FALSE
      )
    })

  failed_periods <- periods[
    map_lgl(meeting_results, \(x) !is.null(x$error))
  ]

  df_meeting_activities <- meeting_results |>
    map("result") |>
    compact() |>
    list_rbind()

  if (is.null(df_meeting_activities) || nrow(df_meeting_activities) == 0) {
    return(list(
      spoken_items = tibble(),
      diagnostics = list(
        pad_intern = pad_intern,
        mp_name = mp_name,
        mp = mp,
        unmatched_meetings = unique(df_plenary$meeting_url),
        failed_items = character(),
        failed_periods = as.character(failed_periods)
      )
    ))
  }

  joined <- df_plenary |>
    distinct(meeting_url) |>
    mutate(
      url_meeting_norm = meeting_url |>
        str_replace("/sitzung/", "/gegenstand/") |> #assumption is "equivalence" of urls
        str_remove("\\?.*")
    ) |>
    left_join(
      df_meeting_activities,
      by = c("url_meeting_norm" = "url_meeting")
    )

  unmatched_meetings <- joined |>
    filter(is.na(url_item)) |>
    pull(meeting_url) |>
    unique()

  item_urls <- joined |>
    filter(!is.na(url_item)) |>
    distinct(url_item)

  item_results <- item_urls$url_item |>
    map(safely(get_item_details))

  failed_items <- item_urls$url_item[
    map_lgl(item_results, \(x) !is.null(x$error))
  ]

  df_item_details <- item_results |>
    map("result") |>
    compact() |>
    list_rbind()

  if (
    is.null(df_item_details) ||
    nrow(df_item_details) == 0 ||
    !"speeches" %in% names(df_item_details)
  ) {
    return(list(
      spoken_items = tibble(),
      diagnostics = list(
        pad_intern = pad_intern,
        mp_name = mp_name,
        mp = mp,
        unmatched_meetings = unmatched_meetings,
        failed_items = failed_items,
        failed_periods = as.character(failed_periods)
      )
    ))
  }

  spoke_items <- df_item_details |>
    filter(!map_lgl(speeches, is.null)) |>
    unnest(speeches) |>
    filter(str_detect(speaker, fixed(mp, ignore_case = TRUE))) |>
    distinct(item_url)

  spoken_items <- df_item_details |>
    semi_join(spoke_items, by = "item_url") |>
    distinct(item_url, .keep_all = TRUE) |>
    mutate(
      pad_intern = pad_intern,
      mp_name = mp_name,
      mp = mp,
      .before = 1
    )

  list(
    spoken_items = spoken_items,
    diagnostics = list(
      pad_intern = pad_intern,
      mp_name = mp_name,
      mp = mp,
      unmatched_meetings = unmatched_meetings,
      failed_items = failed_items,
      failed_periods = as.character(failed_periods)
    )
  )
}

plot_mp_topic_comparison <- function(
  pad_interns,
  top_n = 4,
  min_label_pct = 0.05,
  cache_path = "vignettes/data/mp_topic_profiles.rds",
  refresh = FALSE
) {
  pad_interns <- as.character(pad_interns)

  if (!refresh && file.exists(cache_path)) {
    cached <- readRDS(cache_path)

    if (!setequal(cached$pad_interns, pad_interns)) {
      stop(
        "Cached topic profiles were created for different pad_intern values. ",
        "Re-run with refresh = TRUE to update the cache.",
        call. = FALSE
      )
    }
  } else {
    collected <- pad_interns |>
      map(collect_mp_spoken_items)

    cached <- list(
      pad_interns = pad_interns,
      spoken_items = collected |>
        map("spoken_items") |>
        list_rbind(),
      diagnostics = collected |>
        map("diagnostics")
    )

    dir.create(dirname(cache_path), recursive = TRUE, showWarnings = FALSE)
    saveRDS(cached, cache_path)
  }

  spoken_items <- cached$spoken_items

  if (is.null(spoken_items) || nrow(spoken_items) == 0) {
    stop("No spoken item topics were available for the requested MPs.", call. = FALSE)
  }

  topic_counts <- spoken_items |>
    filter(!map_lgl(topics, is.null)) |>
    unnest(topics) |>
    filter(!is.na(topics), topics != "") |>
    count(mp, topics, name = "n")

  top_topics <- topic_counts |>
    group_by(mp) |>
    slice_max(n, n = top_n, with_ties = FALSE) |>
    ungroup() |>
    distinct(mp, topics)

  plot_data <- topic_counts |>
    left_join(top_topics |> mutate(keep = TRUE), by = c("mp", "topics")) |>
    mutate(topic_label = if_else(is.na(keep), "Other", topics)) |>
    summarise(n = sum(n), .by = c(mp, topic_label)) |>
    mutate(pct = n / sum(n), .by = mp)

  topic_order <- plot_data |>
    filter(topic_label != "Other") |>
    summarise(total = sum(n), .by = topic_label) |>
    arrange(desc(total)) |>
    pull(topic_label)

  mp_order <- cached$diagnostics |>
    map_chr("mp")

  plot_data <- plot_data |>
    mutate(
      topic_label = factor(topic_label, levels = c(topic_order, "Other")),
      mp = factor(mp, levels = mp_order)
    )

  topic_colors <- setNames(
    c(
      colorRampPalette(RColorBrewer::brewer.pal(8, "Set2"))(length(topic_order)),
      "#cccccc"
    ),
    c(topic_order, "Other")
  )

  plot <- ggplot(plot_data, aes(x = mp, y = pct, fill = topic_label)) +
    geom_col(position = position_stack(reverse = TRUE), width = 0.6) +
    geom_text(
      aes(label = if_else(pct >= min_label_pct, percent(pct, accuracy = 1), "")),
      position = position_stack(vjust = 0.5, reverse = TRUE),
      size = 3,
      colour = "white",
      fontface = "bold"
    ) +
    scale_fill_manual(values = topic_colors, name = NULL) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    coord_flip() +
    labs(
      x = NULL,
      y = NULL,
      title = "Topical focus of plenary speeches",
      subtitle = paste0(
        "Top ",
        top_n,
        " topics per MP; remaining topics grouped as 'Other'"
      )
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title.position = "plot",
      legend.position = "bottom",
      legend.key.size = grid::unit(0.45, "cm"),
      panel.grid.major.y = element_blank()
    ) +
    guides(fill = guide_legend(nrow = 2))

  list(
    plot = plot,
    plot_data = plot_data,
    spoken_items = spoken_items,
    diagnostics = cached$diagnostics
  )
}
```

The cache can be refreshed manually when the underlying parliamentary data should be updated.

```{r}
#| label: refresh-mp-topic-cache
#| eval: false

result <- plot_mp_topic_comparison(
  pad_interns = c(14795, 2344, 83409),
  refresh = TRUE
)
```

The rendered article uses the cached data, so the pkgdown build does not need to query the API.

```{r}
#| label: mp-topic-comparison

result <- plot_mp_topic_comparison(
  pad_interns = c(14795, 2344, 83409)
)

result$plot
```
