---
title: "ParlAT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ParlAT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{css, echo=FALSE}
.main-container {
    max-width: 600px !important;
}

pre {
  max-height: 800px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
pre code {
  white-space: pre
}
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# options(tibble.print_min = 4L, tible_print_max=Inf, tibble.width = Inf) 
options(width=10000)
```

```{r setup}
library(ParlAT)
library(dplyr)
```

This vignette provides an introduction how to use the ParlAT package in 
order to the access and subseqently analyze the Open Data provided by
the Austrian Parliament.


# Get mandates

Get the mandates of one or more individuals. Each row in the returned
tibble represents data on one specific mandate.

```{r}
#| code-summary: "Get all mandates"
get_mandates(names=c("Kogler Werner", "Nehammer Karl", "Götze Elisabeth", "Beck Pia Philippa", "Strache Pia Philippa"), institution = "all")
```

```{r}
get_mandates(names=c("Strache Pia Philippa"), institution = "all")
get_mandates(names=c("Beck Pia Philippa"), institution = "all")

```

# Get names
```{r}
get_names(44127)
```

# Get MPs

Get all female MPs of the FPÖ.

Note the importance of the `make_unique` argument. By default, the API of the Parliament
returns a row fo each unqiue MP name. However, since MPs can change their 
name, a standard query returns multiple rows for the same MP. The `make_unique` argument
takes care of this duplications and returns only one row per MP identifier (pad_intern) and
returns the different name variants as a list.

```{r}
df <- get_mps(institution="Nationalrat", party = "FPÖ", gender="female", make_unique = FALSE)
df %>%
filter(pad_intern==14693)

df_unique <- get_mps(institution="Nationalrat", party = "FPÖ", gender="female", make_unique = TRUE)

df_unique %>%
filter(pad_intern==14693) 
```




