---
title: "ParlAT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ParlAT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{css, echo=FALSE}
.main-container {
    max-width: 600px !important;
}

pre {
  max-height: 800px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
pre code {
  white-space: pre
}
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# options(tibble.print_min = 4L, tibble_print_max=Inf, tibble.width = Inf)
options(width = 10000)
```

```{r, setup, include=FALSE}
if (!requireNamespace("ParlAT", quietly = TRUE)) {
  devtools::load_all()
} else {
  library(ParlAT)
}
library(dplyr)
library(ggplot2)
library(tidyr)
library(tidytext)
library(ggtext)
```

This vignette provides an introduction on how to use the {ParlAT} package 
to access and subseqently analyze open data provided by
the Austrian Parliament. Below are some examples which are meant to give
a general overview of the package's functionality.
For details, please consult the [reference section](../reference/index.html).

# Get current MPs in the National Council (Nationalrat)

Let's start with retrieving the compostion of the National Council (Nationalrat) 
at the time of writing (`r format(Sys.Date(), "%d %B %Y")`). This is done 
by the function `get_mps_current()`. 

```{r}
df_current <- get_mps_current(institution = "NR", echo=TRUE)
nrow(df_current)

df_current %>%
count(party, sort=T)
```

If we want to get the composition of a chamber in the past,
the function `get_mps()` comes into play. It either returns all MPs of the
requested chamber, who formed part of it in the course of the entire legislative period (`legis_period` argument), or at a specific date (`date` argument). The latter is a convenient way
to get the composition of the NR at a specifc date. 

Note that the `legis_period` filter is not applicable when searching MPs of Federal Council (Bundesrat). This limitation includes also searches for MPs across all chambers.

```{r}
#Search for all MPs in the National Council as of 1 January 2025
mps_01012025 <- get_mps(date="01.01.2025", institution="NR")
glimpse(mps_01012025)
```

`get_mps` returns one row per MP and legislative period. The list column
`mp_details` contains details on an MPs mandate during
the relevant legislative period. Since such details can change over 
the course of a legislative period (e.g. party affiliation, electoral list of
the mandate), unnesting `mp_details` may result in more than one row
per MP. The example below reveals the changing 

```{r}
#get all MPs of the 26th legislative peiod
mps_legis26 <- get_mps(legis_period=26, institution="NR")

#unnest details on their mandats
mps_legis26 <- mps_legis26  %>%
tidyr::unnest(mp_details)

#Example Alma Zadic during the 26th legislative period
mps_legis26 %>%
dplyr::filter(pad_intern %in% c(2345))
```
 
*Example Federal Council*
```{r, error=TRUE}
#Search for all MPs who were members of the Federal Council during the 25th legislative period:
#An error is returned since legis_period is no applicable filter for institution="BR".
df_mps_25_br <- get_mps(legis_period=25, institution="BR")

#Get start and ending date of legislative period 25 with an auxilary function.
get_legis_periods(legis_period=25)

#Get members of the Federal Council as of 30 September 2013.
df_mps_25_br_date <- get_mps(date="30.10.2013", institution="BR")
nrow(df_mps_25_br_date)
```


# Get mandates

`get_mandates()` returns all current and previous mandates of one or more individuals.
The function takes names as well as unique identifiers (`pad_intern`) as inputs, with the 
latter being the more specific option. 

```{r}
#Example with MP names:
get_mandates(name = c(
  "Karl Nehammer",
  "Andreas Babler"
))

#Example with pad_intern and auxiliary function `get_pad_intern`.
get_pad_intern("Peter Pilz")
get_mandates(pad_intern=1210)
```

The function `get_mandates` also allows us to relatively easily calcualte the total number of days
which the current MPs in the National Council have been serving as of now,
and identify the longest serving MPs (top 5 are shown below).
```{r}
df_mandates <- get_mandates(pad_intern=df_current$pad_intern, institution = "NR")

#keep only MP mandates in the National Council (NR); `instituiton` refers only to the 
#current position, not the preceding mandates.
df_mandates <- df_mandates %>%
  filter(position_code == "NR") 
  
df_mandates <- df_mandates %>%
mutate(position_date_end=case_when(
  is.na(position_date_end) & position_active==TRUE ~ lubridate::today(),
  .default=position_date_end
)) %>%
mutate(position_duration_days = as.numeric(difftime(position_date_end, position_date_start, units = "days")), 
.after=position_date_end)

duration <- df_mandates %>%
summarise(position_days_sum=sum(position_duration_days), .by=c("pad_intern", "name")) %>%
arrange(desc(position_days_sum))

duration %>%
slice_head(., n=5)
```

# Get MPs' details 

If we are interested in the work of a specific MP, the fucntion `get_mps_details()`
is the tool of choice. There are three detail types which can be quried:
"activities", "committee", and "plenary".

For a start, let's get a list of all speeches held in the plenary by MP Karlheinz Kopf.
To get his required pad_intern, we can resort to the auxilary function 'get_pad_intern()'
which returns the MP's unique identifier.

```{r}
#get pad_intern of Karlheinz Kopf
get_pad_intern("Karlheinz Kopf")

#get all statements held in the plenary of the National Council by Karlheinz Kopf
df_plenary_kopf <- get_mps_details(pad_intern=2822, detail_type="plenary", house="NR")

df_plenary_kopf %>%
  count(legis_period) %>%
  arrange(legis_period)
```

Note that `get_mps_details` returns all activites, speeches even if the individual
was member of the government bench or member of the houses presidency at this point in time.
The column `position_name` is a list column containing all mandates the indiviudal held *in the
relevant house* at the time of the plenary statement. 

```{r, include=F, eval=F}
#BUG
#why does Karlheinz Kopf feature only 4 speeches as 2nd president of the Nationalrat?
df_plenary_kopf %>%
count(position_name) %>%
tidyr::unnest_longer(position_name)

#statements given as 2PNR and Abg.
df_plenary_kopf %>%
mutate(position_n=map_dbl(position_name, length)) %>%
filter(position_n>1) %>%
mutate(position_name_chr=map_chr(position_name, \(x) paste(x, collapse=", "))) %>%
select(name, position_name_chr, date, speech_title)

#get mandates of KH Kopf
df_mandates_kopf <- get_mandates(name="Karlheinz Kopf")

df_mandates_kopf_2pnr <- df_mandates_kopf %>%
filter(position_code=="2PNR") 

df_mandates_kopf_2pnr$position_date_start
df_mandates_kopf_2pnr$position_date_end

#Get all statements during presidency
#indeed, there are only 4 plenary statements by Kopf during his time as 2PNR
df_plenary_kopf %>%
filter(between(date, df_mandates_kopf_2pnr$position_date_start, df_mandates_kopf_2pnr$position_date_end))
```


```{r}
#Example Sebastian Kurz: statements held by Sebastian Kurz in the plenary of the National Council.
#Note different positions.

get_pad_intern("Sebastian Kurz")

df_plenary_kurz <- get_mps_details(pad_intern=65321, detail_type="plenary", house="NR") 
```


```{r, include=F, eval=F}
#Check
#Example of get_mps_details with Sebastian Kurz, highlighting different positions
get_pad_intern("Sebastian Kurz")

df_plenary_kurz <- get_mps_details(pad_intern=65321, detail_type="plenary", house="NR") %>%
  mutate(position_name_chr=map_chr(position_name, \(x) paste(x, collapse=", "))) %>%
  mutate(position_name_n=map_dbl(position_name, \(x) length(x)))

df_plenary_kurz %>%
filter(position_name_n>1) %>%
select(
  name,
  position_name_chr,
  legis_period,
  date,
  speech_title
)

#reveals that there were speeches made by Kurz where he was Abg as well as Kanzler or Minister?
#probably speech was held on day when moving between madates; get_mandates returns overlapping intervals
#2017-12-20 positions: ABG and BK; but BK since 2017-12-18; in mandates: MP from 2017-11-09 to 2018-01-22;
get_mandates(name="Sebastian Kurz")
```

# Items under consideration ('Verhandlungsgegenstände')

The ability to search for different items under consideration is probably
one of the most encompassing features offered by the Open Data repository of the
Austrian Parliament (see <a href="https://www.parlament.gv.at/recherchieren/gegenstaende/index.html?FP_001NRBR=NR" target="_blank" rel="noopener">here</a>).
The items which can be queried comprise a wide range including Topical Debates (*Aktuelle Stunden*), Inquiries (*Anfragen*), Government Bills (*Regierungsvorlagen*) etc. All items can be accessed via the general `get_items()` functions. For a full list of available items see [here](../reference/get_items.html#item-gegenstand-). 

For some of these items, additional parameter(s) are available to further
specifiy the query. E.g. the item "ANTR" (Anträge, Motions) allows for 
the specification of the type of motion via the `doc_type` attribute. For 
details see the reference section [here](../reference/get_items.html#doc-type-art-des-antrages-).


*Example: Inquiries (Anfragen)*

Below, as an example, let's query all written and oral questions (*Anfragen*) from the
20 to the 27 legislative period (for the relevant item abbreviations see the function reference), and subsequently visualise the count by party and legislative period.
 
```{r, include=T, eval=T, cache=TRUE, name="get_questions"}
#get items
df_items <- get_items(item = "J_JPR_M", legis_period = seq(20,27), echo=TRUE)

dplyr::glimpse(df_items %>% head())
```

There were in total `r nrow(df_items) |> scales::number()` questions submitted in writing and asked orally by the
members of the National Council from the 20th to 27th legislative period. With a few additional steps, we can easily visualise the results.

```{r, fig.width=10, out.width="100%", cache=TRUE, dependson="get_questions"}
# Create color mapping for Austrian political parties
party_colors <- c(
  "SPÖ" = "#CE000C",
  "ÖVP" = "#63C3D0",
  "FPÖ" = "#0056A2",
  "F" = "#0056A2",
  "F-BZÖ" = "#0056A2",
  "GRÜNE" = "#88B626",
  "NEOS" = "#E3257B",
  "NEOS/NEOS-LIF" = "#E3257B",
  "Grüne" = "#88B626",
  "STRONACH" = "#F47100",
  "BZÖ" = "#F47100",
  "LIF" = "#FFD200",
  "L" = "#FFD200",
  "FRANK" = "#800080",
  "JETZT/PILZ"="lightgrey",
  "OK" ="grey"
)

#aggregate result; account for chaning ÖVP party colors
df_plot <- df_items %>%
  unnest_longer(parl_group) %>%
  count(legis_period, parl_group) %>%
  mutate(
    parl_group_color = case_when(
      parl_group == "ÖVP" & as.numeric(legis_period) < 26 ~ "black",
      parl_group == "ÖVP" & as.numeric(legis_period) >= 26 ~ "#63C3D0",
      TRUE ~ party_colors[parl_group]
    )
  )  

#plot
df_plot %>%
  ggplot()+
  labs(
    title = stringr::str_to_title("Austrian National Council: Number of questions submitted by party ('Anfragen')"),
    subtitle = "Questions submitted from the 20th to 27th legislative period. Questions submitted by multiple parties are counted for each party.",
    caption = "Data: https://www.parlament.gv.at/recherchieren/open-data; retrieved via ParlAT package."
  )+
  geom_bar(aes(x=tidytext::reorder_within(parl_group, -n, legis_period), y=n, fill=parl_group_color), stat="identity")+ 
  scale_x_reordered(guide = guide_axis(n.dodge = 2), continuous.limits=c(1,7))+
  scale_y_continuous(labels=scales::label_number(big.mark = ".", decimal.mark = ","))+  
  scale_fill_identity()+
  facet_wrap(vars(legis_period), scales = "free_x", labeller = labeller(legis_period = function(x) ifelse(x == min(x), paste("Legislative Period", x), x)))+
  theme_minimal()+
  theme(
    strip.text.x= element_text(face = "plain", hjust = 0,color="grey30"),
    panel.grid.minor =  element_blank(),
    panel.grid.major.x=  element_blank(),
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.text.x=element_text(size=rel(0.8)),
    axis.text.y=element_text(size=rel(0.8)),
    axis.title.y=element_blank(),
    plot.caption = element_text(color="grey30", size=rel(.8)),
    plot.subtitle=ggtext::element_textbox_simple(color="grey30", margin = ggplot2::margin(b = 10)),
    plot.title.position = "plot",
    plot.title = element_text(face = "bold")
  )
```

```{r, eval=F, include=F}
With a bit of additional data wrangling, and making use of the 'topic' 
column in the returned data frame, we can also obtain the number of
questions (Anfragen) submitted and posed by each party, and the pertaining
combinations of parties.

df_items <- df_items %>%
  dplyr::mutate(fraktionen_li = stringr::str_extract_all(
    fraktionen, stringr::regex('\\"[^,]+\\"')
  )) %>%
  dplyr::mutate(fraktionen_li = purrr::map(fraktionen_li, unique)) %>%
  dplyr::mutate(fraktionen_n = purrr::map_dbl(fraktionen_li, length)) %>%
  dplyr::mutate(themen_li = stringr::str_extract_all(
    themen, stringr::regex('\\"[^,]+\\"')
  )) %>%
  dplyr::mutate(themen_li = purrr::map(themen_li, unique)) %>%
  dplyr::mutate(themen_n = purrr::map_dbl(themen_li, length))

# df_items %>%
#   ggplot2::ggplot(.,ggplot2::aes(x = fraktionen_li, fill = `doktyp_lang`)) +
#   ggplot2::geom_bar() +
#   ggupset::scale_x_upset() +
#   theme_minimal()

# df_items %>%
#   tidyr::unnest_longer(col = "fraktionen_li") %>%
#   tidyr::unnest_longer(col = "themen_li") %>%
#   ggplot2::ggplot(aes(x = themen_li, fill = fraktionen_li)) +
#   ggplot2::geom_bar() +
#   theme_minimal() +
#   facet_wrap(vars(`doktyp_lang`))
```

*Example: Government Bills ("Regierungsvorlagen")*

As another example to demonstrate the power of the `get_items()` function, let's
get the number of government bills tabled from the 20th to the 27th
legislative period and count them. Furthermore, making use of the `topic` column,
which is returned by the API, one can easily differentiate between the bills' 
various topical foci and obtain the pertaining subtotals.

```{r, fig.width=10, out.width="100%", cache=TRUE}
df_govBills <- get_items(item = "RV", legis_period = seq(20,27)) 

glimpse(df_govBills %>% head())

#count number of bills by legis period
df_govBills %>%
count(gp_code, name = "n") 

df_govBillsTopicsTop5 <- df_govBills %>%
unnest_longer(themen) %>%
group_by(gp_code) %>%
mutate(themen=forcats::fct_lump_n(themen, n = 5, ties.method = "first")) %>%
ungroup() %>%
count(gp_code, themen)

df_govBillsTopicsTop5 %>%
filter(themen!="Other") %>%
ggplot()+
labs(
  title="Austrian Parliament: Number of tabled government bills by topic",
  subtitle="Top-5 topics per frequency and legilslative period. 20th to 27th legislative period. A bill with multiple topics is counted in \neach topic category.",
  caption = "Data: https://www.parlament.gv.at/recherchieren/open-data; retrieved via ParlAT package."
)+
geom_bar(
  aes(y=tidytext::reorder_within(themen, n, gp_code), 
  x=n,
  fill=themen),
  stat="identity")+
scale_y_reordered()+
scale_x_continuous(
  expand=expansion(mult=c(0,.1))
)+
scale_fill_viridis_d()+
facet_wrap(
  vars(gp_code), 
  labeller = labeller(gp_code = function(value) ifelse(value == min(value), paste("GP", value), value)),
  scales="free_y")+
theme_minimal()+
theme(
    strip.text.x= element_text(face = "plain", hjust = 0, color="grey30"),
    panel.grid.minor =  element_blank(),
    panel.grid.major.y=  element_blank(),
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.text.x=element_text(size=rel(0.8)),
    axis.text.y=element_text(size=rel(0.8)),
    axis.title.y=element_blank(),
    plot.caption = element_text(color="grey30"),
    plot.subtitle=ggtext::element_textbox_simple(color="grey30", margin = ggplot2::margin(b = 15)),
    plot.title.position = "plot",
    plot.title = element_text(face = "bold")
  )
```

*Example: Popular Initiatives ("Volksbegehren")*

Get the number of popular initiatives ("Volksbegehren") which were considered
- in different stages - by the Austrian National Counil from the 20th to the 27th
legislative period and count them per legislative period.

```{r, cache=TRUE}
df_volkbg <- get_items(item = "VOLKBG", legis_period = seq(20, 27), institution = "NR", echo = TRUE)
```

# Get names

`get_names` is an auxiliary function to get an MP's different names (due
to marriage, divorce, or other reasons). Below an example with
MP Pia Pilippa Beck, ex Strache.

```{r}
#get first the pad_intern of the MP
get_pad_intern("Strache")
#get all name variants
get_names(pad_intern=44127)
``` 

Providing a date, returns the applicable name at the specified date.
```{r}
get_names(44127, date = "01/01/2024")
``` 


# Miscallaneous

The *echo argument*: Whenever relevant and feasible, ParlAT functions
provide the option to echo the query to the API. The echo prints the 
query's search arguments as well as the resulting URL to the console. The
latter links to the same results on the website of the Austrian Parliament.
The echo argument was included to double-check the results, facilitate
convenient sharing of queries, and provide an additional avenue to explore
the data.
