---
title: "ParlAT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ParlAT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{css, echo=FALSE}
.main-container {
    max-width: 600px !important;
}

pre {
  max-height: 800px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
pre code {
  white-space: pre
}
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# options(tibble.print_min = 4L, tibble_print_max=Inf, tibble.width = Inf)
options(width = 10000)
```

```{r setup}
library(ParlAT)
library(dplyr)
```

This vignette provides an introduction how to use the ParlAT package in 
order to the access and subseqently analyze the Open Data provided by
the Austrian Parliament.


# Get mandates

Get the mandates of one or more individuals. Each row in the returned
tibble represents data on one specific mandate.

code-summary: "Get all mandates"
```{r}
get_mandates(name = c(
  "Stephanie Krisper",
  "Karl Nehammer",
  "Elisabeth Götze"
))
```

```{r}
get_mandates(name = c("Pia Philippa Strache"))
get_mandates(name = c("Pia Philippa Beck"))
```

# Get names
```{r}
get_names(44127, date = "01/01/2024")
get_names(44127, date = "01/01/2023")
get_pad_intern("Strache")
```

# Get MPs

Get all female MPs of the FPÖ.

Note the importance of the `make_unique` argument. By default, the API of the Parliament
returns a row fo each unqiue MP name. However, since MPs can change their 
name, a standard query returns multiple rows for the same MP. The `make_unique` argument
takes care of this duplications and returns only one row per MP identifier (pad_intern) and
returns the different name variants as a list.

```{r, eval=T}
get_mps(institution = "NR", party = "FPÖ", gender = "female", echo = TRUE)
```

# get_items()

The `get_items` function is probably the most comprehensive function of this package. It facilitaes
access to wide range of items 

#| code-summary: "get_items example: get "

```{r}
df_items <- get_items(item = "J_JPR_M", legis_period = 28)


df_items <- df_items %>%
  dplyr::mutate(fraktionen_li = stringr::str_extract_all(
    fraktionen, stringr::regex('\\"[^,]+\\"')
  )) %>%
  dplyr::mutate(fraktionen_li = purrr::map(fraktionen_li, unique)) %>%
  dplyr::mutate(fraktionen_n = purrr::map_dbl(fraktionen_li, length)) %>%
  dplyr::mutate(themen_li = stringr::str_extract_all(
    themen, stringr::regex('\\"[^,]+\\"')
  )) %>%
  dplyr::mutate(themen_li = purrr::map(themen_li, unique)) %>%
  dplyr::mutate(themen_n = purrr::map_dbl(themen_li, length))

library(ggupset)
library(ggplot2)
library(dplyr)

df_items %>%
  ggplot2::ggplot(aes(x = fraktionen_li, fill = `doktyp_lang`)) +
  ggplot2::geom_bar() +
  ggupset::scale_x_upset() +
  theme_minimal()

df_items %>%
  tidyr::unnest_longer(col = "fraktionen_li") %>%
  tidyr::unnest_longer(col = "themen_li") %>%
  ggplot2::ggplot(aes(x = themen_li, fill = fraktionen_li)) +
  ggplot2::geom_bar() +
  theme_minimal() +
  facet_wrap(vars(`doktyp_lang`))
```


